Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-19 2_SSL_EES/article/article_main.tex
added equation

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/test.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/test.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/test.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/test.pdf}
 \caption{Waterfall diagrams of the loss channels in a generic mid/high-power LED package for 2003 (top panel) and 2010 (bottom panel), normalized to 1 Watt of electric power input (yellow bar on the left). Sub-efficiencies corresponding to each loss channel are listed below each column and described in Section \ref{sec:device_performance_metrics}. Numbers for each loss channel indicate energy losses both in relative terms of input power (in percent) at the point of the channel and absolute values (in Watts). Percentages for red, green and blue loss channels indicate losses of remaining red/green/blue light energy. The following corresponding LED architectures from Figure \ref{fgr:chip_architecture_overview} are shown for reference: 2003 (top panel) – flip-chip with YGAG phosphor; 2010 (bottom panel) – flip-chip with 258 phosphor. Details on phosphors are provided in Table \ref{tab:phosphors} and SI section XX. Overall LED package efficiency is $\eta_L = 5.8\%$ in 2003 and $\eta_L = 12.7\%$ in 2010. Abbreviations: Scat. = Scattering. Source: own elaboration based on data from sources listed in SI, section XX.}
 \label{fgr:waterfall_1}
\end{figure*}

\begin{figure*}[h!]
 \centering
 \includegraphics[width=16.5cm]{2_SSL_EES/article/figures/waterfall_performance_2016.pdf}
 \includegraphics[width=16.5cm]{2_SSL_EES/article/figures/waterfall_performance_2020.pdf}
 \caption{Waterfall diagrams of the loss channels in a generic mid/high-power LED package for 2016 (top panel) and 2020 (bottom panel), normalized to 1 Watt of electric power input (yellow bar on the left). Sub-efficiencies corresponding to each loss channel are listed below each column and described in Section \ref{sec:device_performance_metrics}. Numbers for each loss channel indicate energy losses both in relative terms of input power (in percent) a
 t the point of the channel and absolute values (in Watts). Percentages for red, green and blue loss channels indicate losses of remaining red/green/blue light energy. The following corresponding LED architectures from Figure \ref{fgr:chip_architecture_overview} are shown for reference: 2016 (top panel) – flip-chip with PFS phosphor; 2020 (bottom panel) – flip-chip with SALON phosphor. Details on phosphors are provided in Table \ref{tab:phosphors} and SI section 2. Overall LED package efficiency $\eta_L= 32.5\%$ in 2016, $\eta_L= 38.7\%$ in 2020. Abbreviations: Scat. = Scattering. Source: own elaboration based on data from sources listed in SI, section XX.}
 \label{fgr:waterfall_2}
\end{figure*}

>>>>

The cost model we developed relies on a cumulative approach to yielded cost\cite{becker2001use}. In this approach, the yielded cost of process step $1$ is defined as the ratio between the total cost of step 1 $C_1$ and the yield of step 1 $Y_1$:

\begin{equation}
    C_{Y_1} = \frac{C_1}{Y_1}, \ C_{Y_2} = C_{Y_{2 \rightarrow 3}} - C_{Y_1} = \frac{C_1(1-Y_2)+C_2}{Y_1Y_2}, \ C_{Y_3}=\dots
\end{equation}

This cost metric is cumulative by definition, thus

\begin{equation}
    \sum_i C_{Y_i} = \frac{\sum_i C_i}{\prod_i Y_i}
\end{equation}

Yielded cost per step is dependent on the step order and blind to downstream information \cite{becker2001use}. Additional information on details of the computation of cost metrics and the different manufacturing steps is presented in the Supplementary Information.

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/waterfall_performance_2003.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/waterfall_performance_2010.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/waterfall_performance_2003.pdf}
 \includegraphics[width=17cm]{2_SSL_EES/article/figures/waterfall_performance_2003.pdf}
 \caption{Waterfall diagrams of the loss channels in a generic mid/high-power LED package for 2003, 2010, 2016 and 2020 (top to bottom panels), normalized to 1 Watt of electric power input (yellow bar on the left). Sub-efficiencies corresponding to each loss channel are listed below each column and described in Section \ref{sec:device_performance_metrics}. Numbers for each loss channel indicate energy losses both in relative terms of input power (in percent) at the point of the channel and absolute values (in Watts). Percentages for red, green and blue loss channels indicate losses of remaining red/green/blue light energy. The corresponding LED architectures from Figure \ref{fgr:chip_architecture_overview} are shown for reference: 2003 (top panel) – flip-chip with YGAG phosphor; 2010 (bottom panel) – flip-chip with 258 phosphor; 2016 (top panel) – flip-chip with PFS phosphor; 2020 (bottom panel) – flip-chip with SALON phosphor. Details on phosphors are provided in Table \ref{tab:phosphors} and SI section XX. Overall LED package efficiency is $\eta_L = 5.8\%$ in 2003 and $\eta_L = 12.7\%$ in 2010. Abbreviations: Scat. = Scattering. Source: own elaboration based on data from sources listed in SI, section XX.}
 \label{fgr:waterfall}
\end{figure*}
